\documentclass[]{Resume_template}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Keven}{Zhu}{Software Engineering Student\\
kzhu53@uwo.ca | 647-926-7111\\ 27 Cherrystone Dr, Toronto, Ontario, M2H1R8
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Western University}
\descript{B.Eng in Software Engineering}
\location{London, ON}
Sept 2017 - Present (Expected Apr 2021) \\
{\bf Dean's List} (2017-2018)
\sectionsep


\subsection{A.Y. Jackson Secondary School}
\descript{High School Diploma}
\location{Toronto, ON}
Sept 2014 - Jun 2017

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// {\bf github.com/Keven-Zhu} \\
LinkedIn:// {\bf Keven Zhu} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}

\subsection{Undergraduate}
Data Structures and Algorithms \\
Software Construction \\
Software Design \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Proficient}
Java \textbullet{} C++ \textbullet{} Javascript \textbullet{}
HTML \textbullet{} CSS \\ 
\location{Intermediate}
ASP.NEt \textbullet{} Unity \textbullet{} Sybase \textbullet{} MySQL \textbullet{} C\# \\ Git\\
\location{Basic}
Firebase  \textbullet{} \LaTeX\ \textbullet{} Python \textbullet{} React.Js
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Interests
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Interests}
\subsection{Tech}
Machine Learning \textbullet{} Web Development \\ Android/IOS Development \textbullet{} Big Data
\subsection{Other}
Trumpet Playing \textbullet{} Rock climbing \\ Bouldering \textbullet{} Tennis

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{ITG Canada Corp} \\
\descript{Software Engineer Intern }
\location{Jun 2018 - Aug 2018 | Toronto, ON}
\vspace{\topsep}
\begin{tightemize}
\item Developed web applications using C\#, ASP.NET, Javascript, HTML, and CSS with source code control handled using Git
\item Attended daily stand-ups and sprint reviews
\item Attended code reviews and hosted code demonstrations for clients
\end{tightemize}
\sectionsep

\runsubsection{Ivey Fintech Club} \\
\descript{Back-end Developer }
\location{Sept 2018 - Present | London, ON}
\begin{tightemize}
\item Back-end developer --- wrote code with Javascript for a web-based course rating forum
\item Led team in the planning process for the website
\item Played a pivotal role in re-organizing the team into proper groups for optimal development work flow
\end{tightemize}
\sectionsep


\runsubsection{Western Sunstang Solar Car Club}\\
\descript{Software team member}
\location{Sept 2017 – Present | London, ON}
\begin{tightemize}
\item Worked to create various Arduino-based components to be used in the solar car.
\item Attended testing sessions where components could be tested and fixes could be made
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Social Course Planning Website}\\
\descript{Back-end Developer}
\location{Jan 2019 – Present}
Currently being developed by a team of 15 students using React.Js and Firebase for the back-end and HTML, CSS, and Javascript for front-end. Students can create accounts to plan their schedules and rate courses. Facebook integration provides a social media aspect to the website, allowing students to see what friends are taking.

\sectionsep

\runsubsection{Space Shoot 'em up Game}\\
\location{Jan 2019 – Present}
A video game developed using Unity to create the game assets, game scenes, and UI and C\# for scripts. The player plays as a space ship fighting through an endless wave of enemies.

\sectionsep

\runsubsection{Maximum Power Point Tracking Solar Charging Controller} \\
\location{Jan 2019 - Mar 2019}
An Arduino device monitors the current supplied by the solar panels and adjusts the output current to ensure batteries are charging correctly. Written in the Arduino programming language.

\sectionsep

\runsubsection{GPS Arduino Component}\\
\location{Oct 2017 - Dec 2017}
An Arduino device that tracks the location of the Arduino and outputs the latitude and longitude coordinates. Written in the Arduino programming language.

\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
